\chapter{Design}
\label{Chapter:Design}
Having clearly identified the problem and the motivations behind solving it, coupled with well-defined requirements based on informed research, a design incorporating all these details could be developed. Although the design process is being discussed before the implementation phase, it is important to note that these are only initial designs. Due to the agile methodology, the design and implementation processes are essentially interleaved with one another. This allows for the design of one component to be completed, which can then be implemented and improved upon using stakeholder feedback. The subsequent component design is therefore influenced by the feedback received and erroneous approaches identified from the development of previous components.

The first part of the design process involved coming up with an overall system architecture, which is discussed in section 5.1. However, the first component to be designed would be the database as this is required by almost all other components in the system and should be readily available. In order to develop the database, a level of data collection was also necessary which is briefly touched on throughout this section. Following this, we will look at how the four algorithms were designed to not only work as intended but to also factor system integration.

The remainder of the design section covers user interface design in-depth for each of the significant pages on the system. The consistency of the user interface, as well as design choices such as colours and layouts, are also discussed. Finally, a brief overview of responsive mobile design is provided.

\input{Chapters/5.Design/SystemArchitecture}
\input{Chapters/5.Design/Database}
\input{Chapters/5.Design/DataCollection}
\input{Chapters/5.Design/DataProcessing/DataProcessing}
\input{Chapters/5.Design/UsabilityPrinciples}
\input{Chapters/5.Design/Logo}
\input{Chapters/5.Design/UserInterface}
\input{Chapters/5.Design/ResponsiveDesign}