% !TEX root =  ../Repport.tex

\begin{abstract}
	With technology advancing at an exponential rate and portable technology becoming more and more common, crime such as theft and burglary are at an alarmingly high level. Law enforcing agencies and insurance companies do their best to reunite owners with their valuables or compensate for them. However, if the power of the internet and community initiatives such as neighbourhood watch could be combined through an antitheft social network then crime could be combatted by citizens. A web application which allows users to store their possessions and tag them with a location could help people safeguard the things they value most. If these items are ever to be stolen then the owner can report this by tagging the item with the location it was stolen from and through the power of an online community the recovery of this item can be aided. Additionally, systems such as this protect users from becoming victims of fraud and if they become a victim of theft then the system can help simplify insurance claims. The system implements all this functionality, and more, as well as provide a basis for a live valuable tracking system which could transform the way that common people deal with crime.
\end{abstract}

\renewcommand{\abstractname}{Keywords}
\begin{abstract}
Social, Antitheft, Location, Recovery, Stolen, Valuables
\end{abstract}
\newpage

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
A lot of the work done in this project would not have been possible without the help of the stakeholder of the project. Firstly, a sincere thanks goes out to my project supervisor, Dr. Florin Ciuiciu, without whom this project would not exist and certainly would not be as successful as it has been. He provided the original idea and has continually provided much guidance throughout the initial planning, design and development process. Furthermore, his feedback on the project has helped to improve the final product and expand the project beyond its initial scope. Gratitude is also owed to all the users who assisted in the testing of the project and provided feedback, much of which was implemented, to improve the system since its first prototype.

Without the additional third-party frameworks and services, which reduced the development time, the project would not have been able to achieve all its goals. For this reason, credit is also owed to the companies and developers of these services. The largest of these companies include Google and Facebook. Finally, I would like to thank Taylor Otwell, the developer of the Laravel framework, which allowed the system to reach its full potential.
\end{abstract}

\newpage

\tableofcontents

\newpage
\listoffigures
\addcontentsline{toc}{section}{List of Figures}

\newpage
\listoftables
\addcontentsline{toc}{section}{List of Tables}

\newpage

\pagenumbering{arabic}