\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

We would like to humbly acknowledge a number of individuals who have exhibited great support throughout the development of Fidelis. Firstly, and most importantly, we must extend our utmost gratitude to our project supervisor, without whom this project would not have been possible. His continuous guidance, feedback and insight throughout the project have been crucial to the success of the project. In addition to our supervisor, we must also extend our thanks to the secondary assessors, who will not only mark the project but have provided feedback at regular marking points to guide the development of the project.  We would further like to thank our colleagues and friends who have not only provided feedback, suggestions and support but also humour and distraction when the project work seemed overbearing and unachievable. Without the support of these individuals, named below, it may not have been possible to achieve the quality we sought after. The development of a project very rarely involves reinvention of the wheel, but instead using work carried out by others and adapting it to a new purpose and thus we would like to thank the individuals who helped speed up development by providing their resources. Lastly, a social network such as Fidelis cannot function or be successful without its users and the appropriate test data and hence, we would like to thank all the individuals who signed up on the system and took time to provide us with invaluable data and feedback.

\paragraph{Supervisor} Dr. Matthew Leeke

\paragraph{Assessors} Dr. Till Bretschneider, Dr. Matthew Leeke, Dr. Sascha Ott

\paragraph{Development} Josh Greenwood, Andreas Mueller, Taylor Otwell, Nekrasov Ilya

\paragraph{Testimonials} Josh Greenwood, Hannah McAloone, Elenya McCue, Luke Vincent

\paragraph{Feedback and Support} Aria Ahari, Richard Bettermann, Klaudia Dolinska, Josh Greenwood, Jamie Haworth, Mark Hurdley, Henry Jackson, Jennifer Turvey, Florence Vane